---
title: Intro to STAT 385
author: Yamileth Rodriguez
date: '2020-03-09'
slug: intro-to-stat-385
categories:
  - R
tags: []
description: ~
publishDate: '2020-03-09T01:18:58-05:00'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

In this class, I am learning how to use R to program and create functions. During the first week of the course, we learned basic R syntax in order to prepare us to use this language for its most common function: data modeling. Week 2 consisted of learning R data types, structures, and frames. This ended up leading us to our first homework assignment, where we had emulate a French roulette, write an R function that calculates the number of mortgage payment terms given 3 inputs, and display data from Iris and Coronavirus files.



Week 3 is when it started getting more difficult as we learned if-else statements that required us to use logic to ensure the correct function was being made. I definitely spent more time on this week's hw because of the time spent figuring out how to set up the nested if-else loops into my function. In addition to if-else statements, we learned how to display histograms and scatterplots in R. 

For example, here is a scatter plot of Iris Sepal Length vs. Sepal Width using the Iris flower dataset:

```{r }
plot(formula = Sepal.Width ~ Sepal.Length, data = iris,
     main = "Iris Sepal Length vs. Sepal Width",
     xlab = "Sepal Length", ylab = "Sepal Width", 
     pch = 16, col = "violet")
grid()
```

Week 4 consisted of learning about while and for loops, as well as a brand new concept: vectorizing functions. We learned that this decreased the amount of time it took for a function to run, which optimizes time spent running many functions at once. 

For example, here is a vectorized function that outputs names equal to or longer than 8 letters:

```{r  fig.height=5, fig.width=5, background='grey', paged.print=TRUE, fig.align='center'}
long_names_vec <- function(names) {
  return(names[nchar(names) >= 8])
}

long_names_vec(names = c("alexander", "david", "sebastian",
                         "johnathan", "ha",
              "lincoln", "maximo", "mason",
              "luca", "anthony", "kevin"))

```



Week 5 and up until now is consisting of learning how to use GitHub, RMarkdown, R blogdown, and R studio to create our midterm project which is to create a personal website. Ta-da! 



